Democractic Algorithm: A Novel Approach to Hierarchical Swarm Intelligence\\

### 2020-09-26 VLSID/paper.tex
26_09_report_2

In this section the DA algorithm is benchmarked against 18 standard minimization functions. These functions are described in Table $\ref{tab:1}$. The DA was iterated 20 times on each of these functions and the results were compared against other popular SI algorithms such as Particle Swarm Optimization (PSO), Grey Wolf Optimization (GWO), Multiverse Optimization (MVO) and Cuckoo Search (CS). The metric based results such as mean and standard deviation is listed in Table $\ref{tab:2}$

>>>>

In this section the DA algorithm is benchmarked against 18 standard minimization functions. These functions are described in Table $\ref{tab:1}$. The DA was iterated 20 times on each of these functions and the results were compared against other popular SI algorithms such as Particle Swarm Optimization (PSO), Grey Wolf Optimization (GWO), Multiverse Optimization (MVO) and Cuckoo Search (CS). The metric based results such as mean and standard deviation is listed in Table $\ref{tab:2}$. The experiment was set up on a 64-bit Machine with Ubuntu 20.04, Intel® CoreTM i5-7200U CPU @ 2.50GHz × 4, with a GeForce 940MX/PCle/SSE2 graphic card.
